---
title: "Data Science Day-1"
author: "FAIZUL"
date: "2/22/2022"
output: html_document
---
This is the first day for data science course.
I am Faizul & I'm a wannabe google data scientist.


***Basic plotting
-----------------------

1- Simple plot

```{r}
data("iris")
plot(iris$Sepal.Length,iris$Sepal.Width)
```

2- Histogram

```{r}
hist(iris$Sepal.Length)
```

3- Boxplot

```{r}
boxplot(iris$Sepal.Length~iris$Species)
```

4- Image graph

```{r}
x <- matrix(1:120,12,10)
x
image(x)
```

5- Stripchart
```{r}
stripchart(iris$Sepal.Length)
```

6- qqnorm plot

```{r}
qqnorm(iris$Sepal.Length)
```


***Intermediate plotting
---------------------------

1- Scatter plot

```{r}
plot(iris$Sepal.Length,iris$Sepal.Width,xlab = "Sepal length",ylab="Sepal width",main="Iris dataset" )
```

2- Histogram

```{r}
hist(iris$Sepal.Length)
```

3- Boxplot

```{r}
boxplot(iris$Sepal.Length~iris$Species)
```

4- Image graph

```{r}
x <- matrix(1:120,12,10)
image(x)
```

5- Strip Chart

```{r}
stripchart(iris$Sepal.Length)
```
6- QQnorm plot

```{r}
qqnorm(iris$Sepal.Length)
```
7- Scatter plot

```{r}
plot(iris$Sepal.Length,iris$Sepal.Width,xlab = "Sepal Length",ylab="Sepal Width",main = "Scatter Plot")
```
8- Correlation Plot

```{r}
c <- cor(iris[,-5])
corrplot(c)
```
Correlation plot with mtcars data

```{r}
m <- cor(mtcars)
corrplot(m)
```
8.a- number format

```{r}
corrplot(m,method = "number")
```
8.b- upper plot

```{r}
corrplot(m,method = "number",type = "upper")
```

8.c- Lower plot

```{r}
corrplot(m,method = "number",type = "lower")
```

8.d- Square type

```{r}
corrplot(m,method = "square")
```
square(upper)

```{r}
corrplot(m,method = "square",type="upper")
```

8.e- ellipse

```{r}
corrplot(m,method = "ellipse",type="upper")
```
8.f- Order wise

```{r}
corrplot(m,method = "square",type = "upper",order = "AOE")
```
'AOE' is for the angular order of the eigenvectors.
it actually arrange correlation from higher to correlation



Mixed Corrplot-a

```{r}
corrplot.mixed(m)
```
mixed corrplot-b

```{r}

corrplot.mixed(m,lower = "number",upper = "pie",order="AOE")
```



Clustering

```{r}
corrplot(m,order="hclust",addrect = 3)
```
#addrect means number of cluster


*Another method of making correlation plot

```{r}
install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
chart.Correlation(m,histogram = TRUE,method = "pearson")
```
(***) means very significant
(**) means less significant than (***)
(*) means very less significant

We can also make interactive plot in Rmd ,simply by writing 
interactive 3D code inside Rmd file.


