---
title: "DS with R (Day-2)"
author: "FAIZUL"
date: "3/1/2022"
output: html_document
---
## This notebook is about statistical methods and their use in our research
### **List of basic Statistical methods**
1- Sharpio Wilk's method
2- t.test(Independet,paired)
3- ANOVA (One way ANOVA & Two way ANOVA)
4- ANCOVA
5- MANOVA
6- MANCOVA
7- Wilcoxon rank
8- Mann Whitney U test
9- Correlation (Sprarman & Rank Correlation)
10-Kruskul Walis test
11-Regression(Correlation)
12-PostHoc Analysis(Multiple Comparison of means)


### First check the normal distribution of data

```{r}
iris
hist(iris$Sepal.Length)
qqnorm(iris$Sepal.Length)
x <- density(iris$Sepal.Length)
plot(x)
```
All these plots can tell us visually if data is normally distributed.
Another method to test the normality is Shapiro Wilk's test.
"The Shapiro-Wilk test is a statistical test used to check if a continuous variable follows a normal distribution. The null hypothesis (H0) states that the variable is normally distributed, and the alternative hypothesis (H1) states that the variable is NOT normally distributed."

From Shapiro test we can find P values.
If P value > 0.05 (Significant- Normally distributed)
If P value <= 0.05 (Insignificant- Not normally distributed)

```{r}
shapiro.test(iris$Sepal.Length)
```
 Here I find density and Shapiro test for iris(Sepal length),
 I can also find this for other numerical variables of iris and others.
 
If we want to know if data is normal:

(1) Find the density plot and see if the plot is bell-shaped or not.
(2) Find Shapiro test to know the p-value and then from the p-value
     we can tell if data is normal or not.
(3) Find the qqnorm plot and if data distribution is at 45 degree ,data 
     is normal otherwise it's not.
(4) plot the histogram.If every rectangle of histogram is connected to
     each other then data is normal otherwise it's not.
     
```{r}
z <- density(iris$Sepal.Width)
plot(z)

shapiro.test(iris$Sepal.Width)

qqnorm(iris$Sepal.Width)

hist(iris$Sepal.Width)
```
     
     
##t test
###One sample t test
```{r}
t.test(iris$Sepal.Length,mu=0)
```

###Two sample t test for dependent variable(Two numeric variables should be there)

```{r}
t.test(iris$Sepal.Length,iris$Sepal.Width)
```

### Two sample t.test for independent variable(One is numeric other is binary)

```{r}
x <- subset(iris,iris$Species=="virginica"|
            iris$Species=="setosa")
x
t.test(x$Sepal.Length~x$Species)

```

## paired t test(both variable should be numeric)
```{r}
t.test(iris$Sepal.Length,iris$Sepal.Width,paired = TRUE)
```

### There is a vast concept of ANOVA.First I have to learn the concept...


